\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Local Adaptive Optimization of Time Step}

### 2013-10-29 report/article.tex
Added examples for switch

\subsection{Adapt-on-switch}
Special things to note: How subdivision is done: new fixed (30) or relative (dt / 10)
new fixed: We don't catch it early enough. Maybe something with the explicit
euler, maybe something with the linear model

Relative: We get too fine-grained - maybe related to the above

@@

@@

>>>>

\subsection{Adapt-on-switch}
Special things to note: How subdivision is done: new fixed (30) or relative (dt / 10)
new fixed: We don't catch it early enough. Maybe something with the explicit
euler, maybe something with the linear model. We should catch the error before
it escalates into a state in which we cannot rescue it anymore.

Relative: We get too fine-grained - maybe related to the above
\begin{figure}[H]
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images/switch_multiscale_1fps_relative.png}
        \caption{Relative timestepping ($\Delta t = \frac{\Delta t}{100}$)}
        \label{fig:switch_multi_1fps_relative}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images/switch_multiscale_1fps_absolute.png}
        \caption{Absolute timestepping ($\Delta t = \frac{1}{30}$)}
        \label{fig:switch_multi_1fps_absolute}
    \end{subfigure}
    \caption{Adapt-on-switch simulation of particles distributed with two
    scales using 1 fps}
\end{figure}

@@

interpolation of positions makes the integration more stable since the stepping
is based on a point closer in time

@@

The heuristic dampens the system
